Helixer: Cross-species Gene Annotation Of Large Eucaryotic Genomes Using Deep Learning

### 2020-05-15 paper/main.tex
and now with figuresgit add main.tex :-)

\begin{figure*}[!h]
\label{fig:cov_example_main}
\centerline{\includegraphics[width=\textwidth]{images/cov_examples/cov_example_main}}
\caption{high low accuracty by high low RNAseq support for ref}
\end{figure*}

@@

\begin{figure*}[!h]
\label{fig:average_vs_augustus}
\includegraphics[width=5.6cm]{images/cov_examples/average_vs_augustus}  % should be 8.6 when floats are sorted out right
\caption{A caption}
\end{figure*}

>>>>

\begin{figure*}[!h]
\label{fig:cov_example_main}
\centerline{\includegraphics[width=\textwidth]{images/cov_examples/cov_example_main}}
\caption{Four example helixer predictions in the context of RNAseq data, the reference,
and Augustus' prediction for {\it M. esculenta}. The examples were chosen so
that a) Helixer had high accuracy against the reference and the reference
was supported by the RNAseq data, b) Helixer had high accuracy but the 
reference was not supported by the RNAseq data, c) Helixer had low accuracy
and the reference was supported by the RNAseq data, and d) helixer had low
accuracy but the reference was not supported by RNAseq data. Plotability was
a major secondary consideration. Each subplot shows from top to
bottom i) the natural log of the coverage ("cov", solid) and spliced coverage 
("sc", dotted) + 1, ii) the reference annotation in matrix form, iii) 
Augustus' predictions in matrix form, and iv) Helixer's predictions. The reference
and Augustus have either 0 (white) or 1 (black) for each base pair and category, while
Helixer emits a probability from 0-1 represented via gray-scale. "Ntrn" stand
for intron, and "IG" stands for intergenic.
}
\end{figure*}

@@

\begin{figure*}[!h]
\label{fig:average_vs_augustus}
\includegraphics[width=8.6cm]{images/cov_examples/average_vs_augustus}  % should be 8.6 when floats are sorted out right
\caption{Fraction of bp with color-indicated a) coverage and b) spliced coverage of genomic positions 
broken down by the confusion matrix of Augustus and Helixer's predictions. Categories 
are only displayed if they can be meaningfully compared by examining a) coverage or b) spliced
coverage. The displayed fractions are the averages of the individual fractions for the 
six RNAseq-evaluation species. The left-most bars show cases where the two tools agree, 
while the remaining bars show paired conflicts. "Ntrn" stand
for intron, and "IG" stands for intergenic.}
\end{figure*}
